Reply to Editor

### 2022-03-17 Codes/PrepareResults.rmd
code change and new figures F1 and G1

set.seed(3957)

coef_dt <- 
  lapply(
    c(0.1, 0.5, 0.9), 
    function(x) get_rows_optN(data=prep_coef_dt, value = x, range = .0005)) %>%
  bind_rows() %>%
  # --- select one site from each group --- #
  .[,.SD[sample(.N, size = 1)], by = group]

@@

res_y_dt <-  
  coef_dt %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = group] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield*(1 + m_error)] %>%
  .[, opt_N := round(opt_N)] %>%
  melt(id.vars = c("group", "N", "opt_N"), measure.vars = c("det_yield", "yield")) %>%
  .[, variable := case_when(
    variable == "det_yield" ~ "Yield",
    variable == "yield" ~ "Yield including errors"
  )]

@@

# --- MB function to N --- #
vis_MB_curve <- ggplot(res_y_dt[variable=="Yield"]) +
  geom_line(aes(x=N, y=value, group=factor(group))) +
  geom_point(data= sub_dt, aes(x=opt_N, y=value)) +
  geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist +
  theme(legend.position = "none")

# ggplot(res_y_dt) +
#   geom_smooth(aes(x=N, y=value, color=factor(group))) +
#   facet_wrap(~variable, ncol = 2) +
#   labs(y = "Yield (kg/ha)") +
#   labs(x = "N (kg/ha)") +
#   theme_dist
```

@@

# /*===== Train ML =====*/
temp_var_ls <- c("alpha", "beta", "ymax")

@@

# RF <- 
#   RF_run(
#     reg_data = train_dt,
#     var_ls = temp_var_ls
#   )

@@

# === Yield prediction === #
# --- All N experimental rates --- #
N_rate <- test_dt[,aa_n] %>% unique() %>% sort()
# For illustration purpose, we use site where either 2nd and 4th N rates are actually application
tg_N_rate <- N_rate[c(2,4)]

@@

# --- for predicted yield at five experimental N rates --- #
res_pred <- 
  test_dt %>%
  .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(N_rate)),] %>%
  .[, N := N_rate, by = unique_subplot_id] %>%
  # .[,pred_y_RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  .[,pred_y_BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])]

# === For visualization === #
set.seed(2032)
low <- 
  res_true[aa_n == tg_N_rate[1]] %>%
  get_rows_optN(data=., value = 0.2, range = .005) %>%
  .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
  unique()

high <- 
  res_true[aa_n == tg_N_rate[2]] %>%
  get_rows_optN(data=., value = 0.8, range = .005) %>%
  .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
  unique()

vis_res_true <- res_true[unique_subplot_id %in% c(low, high)]
vis_res_pred <- res_pred[unique_subplot_id %in% c(low, high)]

vis_MB_BRF_y <- 
  ggplot() +
    # --- true yield response curve --- #
    geom_line(
      data=vis_res_true, aes(x=N, y=yield, group=factor(unique_subplot_id))
    ) +
    # --- Predicted yield points --- #
    geom_point(
      data=vis_res_pred, aes(x=N, y=pred_y_BRF, group=factor(unique_subplot_id)), color="red"
    ) +
    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield), color = 'blue') +
    geom_segment(data = vis_res_true[aa_n==N], aes(x = aa_n, xend=aa_n, y = yield, yend=-Inf), linetype = "dashed") +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.position = "none")
```

@@

@@

# === Function for RMSE Calculation === #
rmse_general <-function(preds,actual){ 
  sqrt(mean((actual - preds)^2)) %>%
  round(.,1) %>%
  format(, nsmall = 1)

}

>>>>

set.seed(34864)

coef_dt <- 
  lapply(
    c(0.01, 0.25, 0.5, 0.75, 0.99), 
    function(x) get_rows_optN(data=prep_coef_dt, value = x, range = .0005)) %>%
  bind_rows() %>%
  # --- select one site from each group --- #
  .[,.SD[sample(.N, size = 1)], by = group]

@@

res_y_dt <-  
  coef_dt %>%
  .[rep(1:nrow(.), each = length(seq_N)), ] %>%
  .[, N := seq_N, by = group] %>%
  .[, det_yield := gen_yield_MB(ymax, alpha, beta, N)] %>%
  .[, yield := det_yield*(1 + m_error)] %>%
  .[, opt_N := round(opt_N)] %>%
  melt(id.vars = c("group", "N", "opt_N"), measure.vars = c("det_yield", "yield")) %>%
  .[, variable := case_when(
    variable == "det_yield" ~ "Yield",
    variable == "yield" ~ "Yield including errors"
  )] %>%
  .[,group := case_when(
    group == 0.01 ~ "site 1",
    group == 0.25 ~ "site 2",
    group == 0.5 ~ "site 3",
    group == 0.75 ~ "site 4",
    group == 0.99 ~ "site 5"
    )]

@@

# --- MB function to N --- #
vis_MB_curve <- 
  ggplot(res_y_dt[variable=="Yield"]) +
    geom_line(
      aes(x=N, y=value, color=factor(group)), size=1
    ) +
    geom_point(data= sub_dt, aes(x=opt_N, y=value, alpha = "Yield at EONR"), color = "red", size = 2) +
    # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
    scale_alpha_manual(
      name = NULL,
      values = 1,
      breaks = "Yield at EONR",
      guide = guide_legend(override.aes = list(linetype = 0,
        shape = 16,
        color = "red")
        ) 
    ) +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.title = element_blank()) +
    guides(color=guide_legend(nrow=2, byrow=TRUE))
```

@@

# /*===== Train ML =====*/
temp_var_ls <- c("alpha1", "alpha2", "beta1", "beta2", "ymax1", "ymax2", "theta_1", "theta_2")

@@

RF <- 
  RF_run(
    reg_data = train_dt,
    var_ls = temp_var_ls
  )

@@

# === Yield prediction === #
# --- All N experimental rates --- #
N_rate <- test_dt[,aa_n] %>% unique() %>% sort()
# For illustration purpose, we use site where either 2nd and 4th N rates are actually application
tg_N_rate <- N_rate[c(2,3,4)]

@@

# --- for predicted yield at five experimental N rates --- #
res_pred <- 
  test_dt %>%
  .[aa_n %in% tg_N_rate] %>%
  .[rep(1:nrow(.), each = length(N_rate)),] %>%
  .[, N := N_rate, by = unique_subplot_id] %>%
  .[,RF := predict(RF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  .[,BRF := predict(BRF, newdata = .[, c("N", temp_var_ls), with = FALSE])] %>%
  melt(id.vars = c("unique_subplot_id", "yield", "aa_n", "N"), measure.vars = c("RF", "BRF"))

# find_examples_main  <- 
#   res_pred %>%
#   .[variable == "BRF" & aa_n==N,] %>%
#   .[, y_diff_brf := abs(yield - value)] %>%
#   .[y_diff_brf < 700, unique_subplot_id]

# === For visualization === #
# set.seed(1256)

# low <- 
#   res_true[aa_n == tg_N_rate[1]] %>%
#   get_rows_optN(data=., value = 0.2, range = 0.1) %>%
#   .[unique_subplot_id %in% find_examples_main] %>%
#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
#   .[, unique_subplot_id] %>%
#   unique()

# # length(low)

# medium <-
#    res_true[aa_n == tg_N_rate[1]] %>%
#   get_rows_optN(data=., value = 0.5, range = 0.1) %>%
#   .[unique_subplot_id %in% find_examples_main] %>%
#   # .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1),] %>%
#   .[, unique_subplot_id] %>%
#   unique()

# high <- 
#   res_true[aa_n == tg_N_rate[3]] %>%
#   get_rows_optN(data=., value = 0.9, range = 0.1) %>%
#   .[unique_subplot_id %in% find_examples_main] %>%
#   .[unique_subplot_id %in% sample(unique(unique_subplot_id), size = 1), unique_subplot_id] %>%
#   unique()

# vis_res_true <- res_true[unique_subplot_id %in% c(low, medium, high)]
# vis_res_pred <- res_pred[unique_subplot_id %in% c(low, medium, high)]

# low: *13_41*, 15_34
# medium: *8_41*, 8_42, 27_10
# high: 4_21

vis_res_true <- 
  res_true[unique_subplot_id %in% c("15_34", "8_41", "4_21")] %>%
  .[,site := case_when(
    unique_subplot_id == "15_34" ~ "site 1",
    unique_subplot_id == "8_41" ~ "site 2",
    unique_subplot_id == "4_21" ~ "site 3",
    )]

vis_res_pred <- 
  res_pred[unique_subplot_id %in% c("15_34", "8_41", "4_21")] %>%
  .[,site := case_when(
    unique_subplot_id == "15_34" ~ "site 1",
    unique_subplot_id == "8_41" ~ "site 2",
    unique_subplot_id == "4_21" ~ "site 3",
    )]

vis_MB_BRF_y <- 
  ggplot() +
    # --- true yield response curve --- #
    geom_line(
      data=vis_res_true, aes(x=N, y=yield, color = site), size=1
    ) +
    # --- Predicted yield points --- #
    geom_point(
      data=vis_res_pred, aes(x=N, y=value, color = site, alpha = "Predicts"), shape=2, size = 2, stroke = 1
    ) +
    # --- Yield at applied N rate --- #
    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield, alpha = "True yield at actual N rate that was applied"), color = 'blue', size = 2) +
    facet_wrap(~variable) +
    scale_alpha_manual(
      name = NULL,
      values = c(1, 1),
      breaks = c("Predicts", "True yield at actual N rate that was applied"),
      guide = guide_legend(override.aes = list(linetype = c(0, 1),
        shape = c(2, 16),
        color = c("black", "blue")) 
        ) 
    ) +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.title = element_blank()) +
    guides(color=guide_legend(nrow=2, byrow=TRUE))
```

@@

# === Function for RMSE Calculation === #
rmse_general <-function(preds,actual){ 
  sqrt(mean((actual - preds)^2)) %>%
  round(.,1) %>%
  format(, nsmall = 1)
}

@@

### 2022-03-17 Writing/CEA_3rd_round/replies_rev.rmd
some texts added for explaining why yield prediction does not mean good eonr prediction
code change and new figures F1 and G1

Please see Figure H.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round. RMSE is presented in the figure as well. As we have 1000 simulations, it is simply infeasible to present figures like this for all the simulation rounds. But, this figure provides a better sense of the value of RMSE and how good the fit is.

@@

<span style="color:blue">  
Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that this study has no interest in studies that just predict yield without trying to show how they can use it for EONR estimation. Prediction of yield is almost always not the goal of farmers. We are listing studies that predict yields (or estimate yield response function to be more precise) and then predict EOIR based on them. Also, there is no study that test the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We conside those studies not very relevant. Including those studies will simply bloat the introduction. 
</span>

>>>>

<span style="color:blue">  
Please see Figure H.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round. RMSE is presented in the figure as well. As we have 1000 simulations, it is simply infeasible to present figures like this for all the simulation rounds. But, this figure provides a better sense of the value of RMSE and how good the fit is. 
</span>

@@

<span style="color:blue">  
Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that this study has no interest in studies that just predict yield without trying to show how they can use it for EONR estimation. Prediction of yield is almost always not the goal of farmers. We are listing studies that predict yields (or estimate yield response function to be more precise) and then predict EOIR based on them. Also, there is no study that test the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We consider those studies not very relevant. Including those studies will simply bloat the introduction. 
</span>
